Challenges in<br>detecting evolutionary forces<br>in language change <br>using diachronic corpora

### 2018-11-06 evoforces_cletalk/slides.Rmd
better wf animation

library(RColorBrewer)
library(dplyr)
library(plotly)
load("/Users/pplsuser/Dropbox/phd/selection_replypaper/cletalk/binresults.RData")
library(plotly)
load("/Users/pplsuser/Dropbox/phd/selection_replypaper/cletalk/plotlys.RData")
load(file="~/Desktop/korpused/wright-fisher_simulations4.RData")
source("/Users/pplsuser/Dropbox/phd/selection_replypaper/fitmap_plotters.R")

@@

- We evaluated the proposal of Newberry et al. 2017<br>Found that the results are dependent corpus binning, small sample effects, and the specifics of the FIT. 
- Testing vs generating hypotheses; degrees of freedom
--

>>>>

library(RColorBrewer)
library(dplyr)
library(plotly)
load("/Users/pplsuser/Dropbox/phd/selection_replypaper/cletalk/binresults.RData")
load("/Users/pplsuser/Dropbox/phd/selection_replypaper/cletalk/plotlys.RData")
load(file="~/Desktop/korpused/wright-fisher_simulations4.RData")
source("/Users/pplsuser/Dropbox/phd/selection_replypaper/fitmap_plotters.R")

@@

- We evaluated the proposal of Newberry et al. 2017<br>Found that the results are dependent on corpus binning, small sample effects, and the specifics of the FIT. 
- Testing vs generating hypotheses; degrees of freedom
--
